---
title: "Report"
author: "Qitian Ma"
date: "4/17/2020"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup}
library(tidyverse)
library(forecast)
library(lubridate)
library(urca)

raw.ts <- read_csv("EXCSRESNS.csv")

raw.ts$DATE <- date(raw.ts$DATE)
raw.ts$DTBSPCKM <- as.numeric(raw.ts$EXCSRESNS)
raw.ts <- raw.ts[order(raw.ts$DATE), ]

# select year after 2009
raw.ts <- raw.ts[300:length(raw.ts$DATE),]
raw.ts <- ts(raw.ts$EXCSRESNS, start=c(2009,1), freq=12)
```

1. First we need to test the existence of unit root. The ADF test does not rule out the existence of unit root under 5% significance level (-1.6508 > -3.43). After first difference, the ADF test rules out the existence of unit oot under 5% significance level (-6.3374 < -3.43). 
```{r cars}
# unit root test
summary(ur.df(raw.ts, type="trend", selectlags="BIC"))
raw.dif.ts <- diff(raw.ts)
summary(ur.df(raw.dif.ts, type="trend", selectlags="BIC"))
```

2. Simple Time Plot    
From the plot, this time series seems stationary, without trend, without seasonality, with cycle.

```{r SimpleTimePlot}
# general plot
autoplot(raw.dif.ts) +
  ggtitle("After frst-differentiation")
```

3. The ACF-PACF plot points to ARMA(1,1) or ARMA(1,3) and shows not seasonality or unit root.

```{r AcfPacf}
# plot acf pacf
acf(raw.dif.ts) # MA(1) or MA(3)
pacf(raw.dif.ts) # AR(3)

```

4. The statistics do not support trend or seasonality and suggest ARMA(1,3)

```{r Test}
# trend and seasonality
raw.dif.trend.lin <- tslm(raw.dif.ts~trend+season)

summary(raw.dif.trend.lin)

auto.arima(raw.dif.ts)
```

5. ARMA(1,3) beats Exponential Average  (by RMSE and Diebold/Mariano test)


```{r Model}
# model
arima.mod <- function(x, h){
  temp <- Arima(order=c(1,0,3), x)
  temp2 <- tryCatch(forecast(temp, h=h), error=function(e){print("error"); NA})
  temp2
}

eCV <- tsCV(raw.dif.ts, arima.mod, h=1)
rmseCV <- sqrt( mean( eCV^2,na.rm=TRUE))

exptrend.mod <- function(x, h){
  ses(x, h=1, alpha=0.6)
}

eCV.exp <- tsCV(raw.dif.ts, exptrend.mod, h=1)
rmseCV.exp <- sqrt( mean( eCV.exp^2,na.rm=TRUE))

rmseCV < rmseCV.exp

# Diebold/Mariano test
res.exp <- ses(raw.dif.ts, alpha=0.6)$res
arima.mod <- arima(raw.dif.ts, order=c(1,0,3))
res.arma <- arima.mod$res
dm.test(res.exp, res.arma, alternative="greater")
summary(arima.mod)
```

6. Prediction Plot    
ARIMA may spit NA since MLE does not necessarily converge. However, from the available data, the prediction result is good.

```{r PredictionPlot}
# Prediction Plot
store <- c()
n=1
while(n<=length(raw.dif.ts)){
  temp <- tryCatch(Arima(order=c(1,0,3), raw.dif.ts[1:n]), error=function(e){NA})
  temp2 <- tryCatch(forecast(temp, h=1), error=function(e){NA})
  store <<- c(store, ifelse(any(is.na(temp2)), NA, temp2$mean))
  n <- n+1
}

store <- ts(store, start=c(2009,2), freq=12) # The first input series is just 2009-1 and the prediction is 2009-2

autoplot(raw.dif.ts) +
  autolayer(store, series="one-step ahead prediction", color="red") +
  ggtitle("True (black) vs Predicted (red)")
```